Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-06-01 SecDev21/paper.tex
adding a todo for Guillaume

@@

Essentially, the function \spark{TCP_Wait_For_Events} releases the mutex to allow for required events to happen. The function \spark{TCP_Update_Events} detects that the event expected outcome is completed by monitoring the changes to the TCP states. Then it updates the specified event to be true in the socket structure, and it raises the desired event to allow the resuming of the user function that requested the event in the first place. Thus, the \spark{TCP_Update_Events} function is called when a segment is being received, and a state change took place. This makes the \spark{TCP_Update_Events} function a perfect candidate to introduce contracts in SPARK and model the possible states after the completion of each event.

To model any possible state-changes upon the reception of a segment in SPARK, the function \spark{TCP_Process_One_Segment} is introduced.
The behavior of \spark{TCP_Wait_For_Events} is modeled by the ghost function \spark{TCP_Wait_For_Events_Proof} shown in \Cref{algo:waitForEvents}. It computes the set of possible final states after the completion of an event by reusing the function \spark{TCP_Process_One_Segment}. Both functions have the same behavior, and thus, the contract of the function \spark{TCP_Wait_For_Events_Proof} is also attached to \spark{TCP_Wait_For_Events}. This ghost function is proved automatically without even a loop invariant thanks to loop unrolling in GNATprove.

>>>>

\todo[inline]{KG to GC : when you are talking about functions you should say where they are located. There will be readers that will want to see the coresponding code in the repository. Look for examples in the HICLASS report: e.g. This is implemented by the Tcp\_Wait\_For\_Events\_Proof function, located in the tcp\_misc\_binding.adb}

Essentially, the function \spark{TCP_Wait_For_Events} releases the mutex to allow for required events to happen. The function \spark{TCP_Update_Events} detects that the event's expected outcome is completed by monitoring the changes to the TCP states. Then it updates the specified event to be true in the socket structure, and it raises the desired event to allow the resuming of the user function that requested the event in the first place. Thus, the \spark{TCP_Update_Events} function is called when a segment is being received and a state change took place. This makes the \spark{TCP_Update_Events} function a perfect candidate to introduce contracts in SPARK and model the possible states after the completion of each event.

To model any possible state changes upon the reception of a segment in SPARK, the function \spark{TCP_Process_One_Segment} is introduced.
The behavior of \spark{TCP_Wait_For_Events} is modeled by the ghost function \spark{TCP_Wait_For_Events_Proof} shown in \Cref{algo:waitForEvents}. It computes the set of possible final states after the completion of an event by reusing the function \spark{TCP_Process_One_Segment}. Both functions have the same behavior, and thus, the contract of the function \spark{TCP_Wait_For_Events_Proof} is also attached to \spark{TCP_Wait_For_Events}. This ghost function is proved automatically without even a loop invariant, thanks to loop unrolling in GNATprove.

@@
